Continuous time

### 2023-10-18 continuous-time.qmd
First draft (#2)
* Download data with R

* Small edits

* Init bibliography

* gitignore Word output

* Move all computation to ms.qmd

* Throw out prose

* WIP pre-holiday changes :smile:

* Update renv

* Ignore output style for now

* Minor code cleaning

* Move code block up

* Small model revision

Also added some verbal description

* rm old file

* move metadata to same file

* Fix metadata

* Estimate full model

* Reparameterize model

* WIP updates

* Fix #5

* Fix build

* WIP changes

* dockerize (#6)

Dockerize the project

Closes #3

* Figure and heterogeneity

* use correct env

In the main analysis in @sec-analyze we focused on contrasting the mood at the beginning of a session with the average mood during session. In this document we focus on two additional research questions:

@@

library(scales)
library(cmdstanr)
library(posterior)
library(brms)
library(patchwork)
library(tidyverse)
library(splines)
library(emmeans)
library(lme4)
library(broom.mixed)
library(knitr)
library(rstanarm)
source("R/functions.R")
source("R/fit_cached.R")
source("R/common.R")
```

@@

```{r}
#| label: fig-intercept-sds
#| fig-cap: Estimated curves for participants with an intercept equal to 0, -1SD, and -2SD.
#| fig-height: 3
#| fig-width: 8
source("R/get_trend.R")

@@

p_pre_x
ggsave(
  "figures/fig-interaction-model.png", 
  p_pre_x, 
  width = 7, 
  height = 5
)
```

Let's also calculate the within-session change for the interaction model.
```{r}
#| label: fig-lmm-pre-interaction-change
#| fig-cap: Within-session change from the interaction model
#| fig-height: 2.5
#| fig-width: 8
source("R/get_change_by_pre.R")
d_x_change <- data.frame(
  pre = pre_values,
  label = pre_labels_x
) |>
  pmap(\(pre, label) get_change_by_pre(
    pre,
    label,
    fit3,
    hours = seq(0, 3, length.out = 100)
  )) |>
  bind_rows()

@@

```{r}
#| label: ggsave-fig-ms-interaction
#| echo: false

ggsave(
  "figures/fig-pre-x-change.png", 
  p_tmp, 
  width = 7, 
  height = 3.5
  )
```

@@

```{r}
#| label: ggsave-fig-ms-no-interaction
#| echo: false

ggsave(
  "figures/fig-change.png", 
  p_tmp, 
  width = 6, 
  height = 3
  )
```

@@

```{r}
#| label: bayes-int-sd
source("R/get_trend_bayes.R")
res <- map(
  pre_sds,
  \(sd) get_trend_bayes(sd = sd)
) |>
  bind_rows() |>
  mutate(
    intercept = factor(
      sd,
      levels = pre_sds,
      labels = pre_labels
    )
  )

>>>>

In the main analysis we focused on contrasting the mood at the beginning of a session with the average mood during session. In this document we focus on two additional research questions:

@@

library(scales)
library(cmdstanr)
library(posterior)
library(brms)
library(patchwork)
library(tidyverse)
library(splines)
library(emmeans)
library(lme4)
library(broom.mixed)
library(knitr)
library(rstanarm)
source("R/functions.R")
source("R/common.R")
```

@@

```{r}
#| label: fig-intercept-sds
#| fig-cap: Estimated curves for participants with an intercept equal to 0, -1SD, and -2SD.
#| fig-height: 3
#| fig-width: 8

@@

p_pre_x
```

Let's also calculate the within-session change for the interaction model.
```{r}
#| label: fig-lmm-pre-interaction-change
#| fig-cap: Within-session change from the interaction model
#| fig-height: 2.5
#| fig-width: 8

d_x_change <- data.frame(
  pre = pre_values,
  label = pre_labels_x
) |>
  pmap(\(pre, label) get_change_by_pre(
    pre,
    label,
    fit3,
    hours = seq(0, 3, length.out = 100)
  )) |>
  bind_rows()

@@

@@

@@

```{r}
#| label: bayes-int-sd

res <- map(
  pre_sds,
  \(sd) get_trend_bayes(sd = sd)
) |>
  bind_rows() |>
  mutate(
    intercept = factor(
      sd,
      levels = pre_sds,
      labels = pre_labels
    )
  )
